High quality content reconstruction in images using a high capacity self-embedding algorithm

### 2014-04-22 Paper/main.tex
Intro sections and some content

\section{Introduction}
A short introduction into the wonderful world of fragile watermarking, self embedding and image recovery. Attempt to make this interesting...
It would also probably be beneficial to mention how the paper will be structured. 
That I will first research the current self embedding and content recovery methods. 
Then mention that I will also research the high capacity embedding algorithms and evaluate their applicability to my current problem. 
I will then start with my experiment and all the things that will contain. 
I will finally analyze my findings and draw conclusions based on my research and my experimental findings. 
This will involve evaluating if the proposed method does indeed increase quality and wasn't just a waste of time. 
Although that would technically be a finding as well.

>>>>

\section{Introduction}
This section gives a brief description of the concepts used in this report.
The reasoning behind the proposed method will also be explained in \ref{introQualityIncrease} and \ref{introHighCap}.
This will serve to to show the applicability of the proposed method as well as the shortcomings it attempts to address.

\subsection{Overview}
Self recovering images (described in \ref{introSelfEmbedRecovery}) poses an interesting problem.
There is an inherent trade-off (described in \ref{introQualityTrade}) between the quality of the image after embedding and the quality of the image after recovery.
This report proposes a method in which a high capacity embedding algorithm (described in \ref{introHighCap}) is applied to the problem of self-recovering images to attempt to increase the quality of the images (described in \ref{introQualityIncrease}) both after embedding and after recovery.

\subsection{Steganography}
\label{introSteganography}
Steganography is the process of hiding information in such a way that it does not get detected \cite{johnson1998exploring}.
Steganography, derived from Greek means "covered writing".
This means it differs from cryptography which does not attempt to hide information but merely scrambles it so it cannot be understood.
Steganography does not scramble the information but rather relies on the information to remain hidden.

\subsection{Fragile Watermarking}
\label{introFragWatermarking}

\subsection{Self embedding and recovery}
\label{introSelfEmbedRecovery}

\subsection{Quality Trade-off}
\label{introQualityTrade}

\subsubsection{Increasing quality with capacity}
\label{introQualityIncrease}

\subsubsection{High capacity embedding algorithms}
\label{introHighCap}
